---
title: "How to draw geologic map"
author: "YiChun Sung"
date: "2017年4月25日"
output: html_document
---

## Library useful packages

```{r, message=FALSE, warning=FALSE}

library(magrittr)
library(ggplot2)
library(leaflet)
library(knitr)
library(maptools) # 協助讀取shp file
library(sp)
library(rgeos) 

```


## 從GitHub引入我的套件

```{r  eval=FALSE}
#install.packages("devtools")
library(devtools)
#install_github("yichunsung/transtwd97")
library(transtwd97)

```


# Get Taiwan region

### Method 1 : read shpfile

use function maptools::readShapeSpatial()

#### Base Taiwan map
```{r, message=FALSE, warning=FALSE}
setwd('c://R_Application/map')
#Sys.setlocale(category = "LC_ALL", locale = "")
TaiwanRegion97_shp <- readShapeSpatial("shpData/Taiwan_region_97TM2/97TM2.shp")
plot(TaiwanRegion97_shp)


```

### Method 2 : Get Data from GADM 

use raster::getData() to get Taiwan map from GADM.org
```{r  eval=FALSE}
library(raster)
twDist0 <- getData('GADM', country='TW', level=0)
twDist1 <- getData('GADM', country='TW', level=1)
twDist2 <- getData('GADM', country='TW', level=2)

plot(twDist1)
```



### fault no.SHP_F0012

read Shp file and use ggplot2::fortify() to transform SpatialPolygonsDataFrame to data frame

```{r, message=FALSE, warning=FALSE}
setwd('c://R_Application/map')
Fault_DJ_shp <- readShapeSpatial("shpData/fault data/SHP_F0012/F0012_TWD97.shp") # 大甲斷層
Fault_DJ_dataFrame <- fortify(Fault_DJ_shp, region = "名稱") # 將SpatialPolygonsDataFrame 轉成Data.Frame (package 來源: ggplot2)

```

```{r  eval=FALSE}
plot(Fault_DJ_shp)

```

```{r, message=FALSE, warning=FALSE}

ggplot_DJ_fault <- ggplot(Fault_DJ_shp)+ geom_map(data = Fault_DJ_dataFrame, aes(map_id = id), col="white", fill="grey", map = Fault_DJ_dataFrame) + expand_limits(x = Fault_DJ_dataFrame$long, y = Fault_DJ_dataFrame$lat)
ggplotly(ggplot_DJ_fault)

```

### 將TWD97 轉換成 WGS84


```{r  eval=FALSE}

Fault_DJ_WGS84 <- TWD97toWGS84(inputTWD97Y = Fault_DJ_dataFrame$lat, inputTWD97X = Fault_DJ_dataFrame$long)

```

### 畫在leaflet map上

```{r  eval=FALSE}
leaflet() %>% addTiles() %>% setView(lng=120.6207, lat=24.33367, zoom = 10) %>%
  addPolygons(lng=Fault_DJ_WGS84$Longitude, lat = Fault_DJ_WGS84$Latitude)

```

### bulit a data.frame for ggplot2 package

Because the shp file is always TWD97 data, we need to use trans97::TaiwanTown_map_WGS84 to convert our data to WGS84 style.

Then, we reset our new data frame as ggplot2::fortify data frame and we can plot our data into ggplot.

However, if you want to show you axis x-y of figure as TWD97 style, you don't need to use trans97::TaiwanTown_map_WGS84. Please just use function fortify to make your new data frame.

```{r  eval=FALSE}
# use gglot2::fortify to make a new data frame
TaiwanTown_map <- fortify(TaiwanRegion97_shp, region = "townname") 

# convert to WGS84
TaiwanTown_map_WGS84 <- TWD97toWGS84(inputTWD97Y = TaiwanTown_map$lat, inputTWD97X = TaiwanTown_map$long)
# cbind id into df
TaiwanTown_map_WGS84 <- cbind(TaiwanTown_map_WGS84, id = TaiwanTown_map$id) 
names(TaiwanTown_map_WGS84) <-c('lat', 'long', 'id')

# reset a fortify style data frame
TaiwanTown_map_WGS84_renew <- data.frame(long = TaiwanTown_map_WGS84$long, lat = TaiwanTown_map_WGS84$lat, order =TaiwanTown_map$order, hole = TaiwanTown_map$hole, piece = TaiwanTown_map$piece, id = TaiwanTown_map$id, group = TaiwanTown_map$group)

```

### Base map for Taiwan

After we bulit a new data frame for WGS84, we can use it to plot a new base map of Taiwan.

Useing function ggplot+geom_map is a easy method to plot a base map.

```{r  eval=FALSE}

TaiwanRegion97 <- ggplot(TaiwanTown_map_WGS84_renew) + 
  geom_map(data = TaiwanTown_map_WGS84_renew, 
           aes(map_id = id), 
           col="black", 
           fill="green", 
           map = TaiwanTown_map_WGS84_renew) + 
  expand_limits(x =TaiwanTown_map_WGS84_renew$long, 
                y =TaiwanTown_map_WGS84_renew$lat)

TaiwanRegion97
```

### leaflet for GIS application

Actually, I think that Only base map is not enough for us because we always want to create fascinating things.

Therefore, package leaflet is a good idea for draw a facinating map.

However, we still need to prepare something before we plot our data into leaflet map.

According to ("https://github.com/rstudio/leaflet/issues/232"), we knew that we could use this function to change the data frame to an sp::SpatialPolygons object, which works nicely with Leaflet. 

Now, we bulid a new function to create a new SpatialPolygons.

This best function is not my idea. It's from jcheng5 .
```{r  eval=FALSE}
library(dplyr)
library(sp)
library(leaflet)

dataframeToPolygons <- function(df, latCol, lngCol, idCol) {
  SpatialPolygons(lapply(unique(df[[idCol]]), function(id) {
    Polygons(list(Polygon(as.matrix(
      df[df[[idCol]] == id, c(lngCol, latCol)]
    ))), id)
  }))
}

changetoPolygons <- dataframeToPolygons(TaiwanTown_map_WGS84_renew, "lat", "long", "group")
```


```{r  eval=FALSE}
leaflet(changetoPolygons) %>% 
  addProviderTiles("Esri.WorldImagery")%>%
  setView(lng=120.6207, lat=24.33367, zoom = 8)%>%
  addPolygons( fillColor = "yellow", 
               weight = 2,                             
               opacity = 1,                             
               color = "black",                             
               dashArray = "3",                             
               fillOpacity = 0.3
              )


```
